### 2018-12-12 Chapters/Chapter2.tex
cites

We will consider a half filled system in the strong coupling limit. Ignoring electron hopping and spin orbit interaction, the ground state of this system is massively degenerated. We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace. This effective Hamiltonian will be the sum of a spin exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$ plus an anisotropic interaction of the form $\bs{D}\bs{S}_i\times\bs{S}_j$ \cite{Moriya1960}.

@@

\begin{equation}
\boldsymbol{\Delta}_{ij} = \begin{cases}
             \boldsymbol{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
             0,  & \text{otherwise}
       \end{cases} \quad
\end{equation}

Hubard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.

@@

The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model. Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material. $\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}. In the next chapter we will examine this further. Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.

>>>>

We will consider a half filled system in the strong coupling limit. Ignoring electron hopping and spin orbit interaction, the ground state of this system is massively degenerated. We will find an effective Hamiltonian considering that the hopping term and the spin interaction term act on this subspace. This effective Hamiltonian will be the sum of three spin interactions: an exchange interaction $J\bs{S}_i\bs{S}_j$ with $J>0$, a Dzyaloshinkii-Moriya interaction $\bs{D}\bs{S}_i\times\bs{S}_j$ and an anisotropic interaction $\bs{S}_i \bs{\Gamma} \bs{S}_j$ known as pseudodipolar interaction \cite{Moriya1960}.

@@

\begin{equation}
\bs{\Delta}_{ij} = \begin{cases}
             \bs{\Delta}_{ij},  & \text{for } (i,j) \text{ nearest neighbours} \\
             0,  & \text{otherwise}
       \end{cases} \quad
\end{equation}

Hubbard models with hopping terms further than nearest neighbors are also interesting and will be considered in next chapter.

@@

The $J_{ij}^0\bs{S}_i\bs{S}_j$ term is known as exchange interaction, in the $\bs{\Delta}_{ij} = 0$ limit (no SOI) we see that \ref{HeffNOEMF} reduces to the Heisenberg model. Since $J_{ij}^0 > 0$ this model describes an antiferromagnetic material. However, the Hubbard model can also lead to ferromagnetic and paramagnetic magnetic behavior in non half-filled systems as shown in \cite{Hirsch1985} with a mean-field theory approach. $\bs{D}_{ij}^0 \bs{S}_i \times \bs{S}_j$ is known as Dzyaloshinskii-Moriya
interaction (DMI), the symmetries of the crystal will restrict the direction of $\bs{D}_{ij}^0$ \cite{Moriya1960}. In the next chapter we will examine this further. Lastly $\bs{S}_i \bs{\Gamma}_{ij} \bs{S}_j$ is an anisotropic term known as pseudodipolar interaction \citep{Moriya1960} and it is usually neglected since it is proportional to $\bs{\Delta}_{ij}^2$.
